%-------------------------
% Resume in Latex
% Author : Abey George
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{lmodern} % ✅ Fix font shape warnings
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{graphicx}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\RequirePackage{tikz}
\RequirePackage{xcolor}
\RequirePackage{fontawesome}
\usetikzlibrary{svg.path}

\definecolor{cvblue}{HTML}{0E5484}
\definecolor{black}{HTML}{130810}
\definecolor{darkcolor}{HTML}{0F4539}
\definecolor{cvgreen}{HTML}{3BD80D}
\definecolor{taggreen}{HTML}{00E278}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\colorlet{name}{black}
\colorlet{tagline}{darkcolor}
\colorlet{heading}{darkcolor}
\colorlet{headingrule}{cvblue}
\colorlet{accent}{darkcolor}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{{#1 \vspace{-2pt}}}
}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{\linewidth}[t]{@{\extracolsep{\fill}}p{0.7\textwidth}r}
      \textbf{\large#1} & \textbf{\small #2} \\
      \textit{\large#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{\linewidth}{@{\extracolsep{\fill}}p{0.75\textwidth}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{flushright}
    {\Huge \scshape Noel Jesudas Thareparambil} \\ \vspace{2pt}
    Thane, Maharashtra \\ \vspace{2pt}
    \small
    \raisebox{-0.1\height}{\faPhone} \href{tel:+919004063351}{\underline{+91-9004063351}} ~
    \raisebox{-0.1\height}{\faEnvelope} \href{mailto:noel.jesudas.t@gmail.com}{\underline{noel.jesudas.t@gmail.com}} ~
    \raisebox{-0.1\height}{\faLinkedin} \href{https://linkedin.com/in/noel-jesudas-774188234}{\underline{Noel Jesudas}} ~
    \raisebox{-0.1\height}{\faGithub} \href{https://github.com/noeljesudas}{\underline{Noel Jesudas}}
\end{flushright}

%-----------SUMMARY-----------
\vspace{6pt}
\section*{SUMMARY}
Aspiring Machine Learning and Python developer currently pursuing a Bachelor's degree in Information Technology. Passionate about building intelligent, data-driven solutions and exploring the intersection of AI and software development. Actively seeking opportunities to apply technical skills in a real-world setting and grow through collaborative innovation.
\vspace{-6pt}

%-----------EDUCATION-----------
\section{EDUCATION}
\resumeSubHeadingListStart
    \resumeSubheading
      {Saraswati Vidyalaya School, G.B Road, Thane(W)}{2019 -- 2020}
      {-\textbf{SSC Percentage} - \textbf{77.8}}{Thane, Maharashtra}
    \resumeSubheading
      {Narayana Jr College, Kolshet, Thane(W)}{2021 -- 2022}
      {-\textbf{HSC Percentage} - \textbf{94.67}}{Thane, Maharashtra}
    \resumeSubheading
      {Fr. C Rodrigues Institute of Technology}{3rd Year Pursuing}
      {-\textbf{Bachelors of Engineering in Information Technology} - \textbf{CGPA - 7.20}}{Vashi, Maharashtra}
\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{PROJECTS}
\resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{\large{Movie Recommendation System}}}{2025}
        \resumeItemListStart
            \resumeItem{Developed a content-based movie recommendation system using TF-IDF vectorization and cosine similarity.}
            \resumeItem{Integrated English and Hindi movies, ensuring a 60:40 dataset balance to address cultural bias.}
            \resumeItem{Fetched and parsed additional Hindi movie data via TMDB API to enhance diversity.}
        \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{\large{Market Basket Analysis}}}{2025}
        \resumeItemListStart
            \resumeItem{Created dynamic visual dashboards using Plotly for support, confidence, and lift.}
            \resumeItem{Collaborated with team members for data mining, visual design, and deployment.}
        \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{\large{Football Web Page for Drishti Technology}} \href{https://football-analytics-rho.vercel.app/}{\underline{Live Site}}}{2025}
        \resumeItemListStart
            \resumeItem{Designed and developed a responsive web app showcasing AI-powered football analytics.}
            \resumeItem{Presented products like MAANVI (match analytics) and Vision Pro (real-time foul detection).}
            \resumeItem{Used scroll-triggered animations with AOS.js for better user engagement.}
        \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{EXPERIENCE}
\resumeSubHeadingListStart
  \resumeSubheading
    {Time Series IoT Datalogger Platform}{06 2025 -- 08 2025}
    {\underline{Full Stack Developer Intern}}{Thane, Maharashtra}
      \resumeItemListStart
        \resumeItem{Tech used: React, FastAPI (Python), MongoDB, ApexCharts}
        \resumeItem{Developed a role-based IoT data logging platform where users can view, analyze, and export sensor readings while admins manage devices, users, and templates.}
        \resumeItem{Implemented REST APIs in FastAPI for authentication (JWT), device assignment, real-time sensor data upload, and logging of admin/user actions.}
        \resumeItem{Built a React frontend with ApexCharts for time-series visualization, supporting zoom, hover-tooltips, and custom time range selection.}
      \resumeItemListEnd
\resumeSubHeadingListEnd
\resumeSubHeadingListStart
    \resumeSubheading
      {Dynamic Water Management System For Multipurpose Usage}{08 2024 -- 12 2024}
      {\underline{Team Member}}{Vashi, Navi Mumbai}
        \resumeItemListStart
            \resumeItem{Tools: LabVIEW 2019, Python, Tkinter, XGBoost}
            \resumeItem{Built a predictive water tank management system using real-time simulation and ML.}
            \resumeItem{Achieved 96\% accuracy using XGBoost to predict remaining water supply and refill time.}
            \resumeItem{Created a user-friendly Tkinter GUI for input and output visualization.}
        \resumeItemListEnd
\resumeSubHeadingListEnd


%-----------TECHNICAL SKILLS-----------
\section{TECHNICAL SKILLS}
\begin{itemize}[leftmargin=0.15in, label={}]
\small{\item{
    \textbf{Languages:} Python, Java, JavaScript, SQL, NoSQL, HTML, CSS \\
    \textbf{Developer Tools:} VS Code, Git, GitHub, AWS, Postman \\
    \textbf{Frameworks:} ReactJS, NodeJS, ExpressJS, Flask
}}
\end{itemize}

%-----------EXTRACURRICULAR-----------
\section{EXTRACURRICULAR}
\resumeSubHeadingListStart
    \resumeSubheading
      {IEEE FCRIT}{08 2024 -- Present}
      {\underline{Assistant Treasurer}}{Vashi}
        \resumeItemListStart
            \resumeItem{Managed budgeting, expense tracking, and financial reporting.}
            \resumeItem{Prepared audit-ready reports for internal and external review.}
        \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------CAREER ASPIRATIONS-----------
\section{CAREER ASPIRATIONS}
\resumeItemListStart
    \resumeItem{Seeking opportunities in Python and Machine Learning to solve real-world problems.}
    \resumeItem{Eager to work on data projects and gain experience deploying ML solutions.}
    \resumeItem{Aspire to contribute to innovative teams building scalable, intelligent systems.}
\resumeItemListEnd

\end{document}
